---
title: "Office of Marketing and Brand Management"
date: "July 10, 2020, (updated `r format(Sys.time(), '%B %d, %Y')`)"

output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: tinytex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(knitr)
library(formatR)
library(blastula)
library(gt)
library(glue)
library(formattable)
library(hms)
library(tidyverse)
library(knitr)
library(ggpubr)
library(lubridate)
library(zoo)
library(forecast)
library(chron)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(tinytex.verbose = TRUE)

```

# __FY21 Transfer Student Application Flow__

# Description


`r newthought('The purpose of this report')` is to revisit the flow of applications to the Transfer programs among 19-24 year olds. This is important because the cadence of this process is different from that of the working adult cohort (years 25 and over). 

# Findings

The table below illustrates the flow of applications among current undergraduates to the Transfer program at the University of Southern Maine (USM), January 1, 2017 - present. 


```{r}
TransferApps <- read.csv("C:/Users/christine.iyer/Box/FY21_Transfer_App_Flow/All_Transfers_Born_Anytime.csv", header = T, stringsAsFactors = F)

 TransferApps <- TransferApps %>% 
  mutate(App.Application.Date = as.Date(App.Application.Date, format = "%m/%d/%Y"), 
                                        Created.Date = as.Date(Created.Date, format = "%m/%d/%Y"), 
                                        Birthdate = as.Date(Birthdate, format = "%m/%d/%Y")) %>%
  select(Email, Primary.City, Primary.State.Province, Primary.County, Birthdate, Created.Date, App.Application.Date, App.Application.Status, Student.Stage)
  
Confirmed <- c("Confirmed", "Withdrawn (After Confirmed)")
Enrolled <- c("Enrolled")
Admitted <- c("Admitted (Not Confirmed)", "Withdrawn (After Admitted)", "Withdrawn (After Decision)")
SortedTransfers <- TransferApps %>% 
  mutate(Stage = ifelse(App.Application.Status == "", "Inquiry", ifelse(App.Application.Status == "Enrolled", "Enrolled", 
                                                                         ifelse(App.Application.Status %in% Admitted, "Admitted", 
                                                                                ifelse(App.Application.Status %in% Confirmed, "Confirmed", "Applied")))))

SortedTransfers <-  SortedTransfers %>% 
  
  group_by(Stage, Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province, Birthdate) %>% summarise(n = n()) %>% spread(Stage, n) %>% select(Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province, Birthdate,Inquiry, Applied, Admitted, Confirmed, Enrolled)


SortedTransfers <- SortedTransfers %>% mutate(AgeAtApp = difftime(App.Application.Date,Birthdate,  units = "weeks"), Age = as.numeric(round(AgeAtApp/52,0)), Age = ifelse(Age < 25, "24 and Under", "25 and Up"))


#tail(SortedTransfers)
SortedTransfers1 <- SortedTransfers %>% 
  filter(Age == "24 and Under") %>% 
  mutate_at(7:11, ~replace(., is.na(.), 0)) %>% 
  mutate(
    Applied = sum(Applied) + sum(Admitted)+ sum(Confirmed) + sum(Enrolled), 
    Admitted = sum(Admitted)+ sum(Confirmed) + sum(Enrolled),
    Confirmed =  sum(Confirmed) + sum(Enrolled),
    Enrolled = sum(Enrolled)) %>% 
  group_by(Age, App.Application.Date) %>% 
  summarise(Applied = sum(Applied)) %>% 
  filter(Applied > 0)


SortedTransfers2 <-  SortedTransfers1 %>%
  na.omit() %>% 
  arrange(App.Application.Date)

colorPalette <- c("#323DA5", "#FFC13D", "#4595A4", "#C55A82" )


SortedTransfers3 <- SortedTransfers1 %>% 
  mutate(Month = as.yearmon(App.Application.Date), 
         Year = year(App.Application.Date), 
         Month_1 = month(App.Application.Date), 
         Month_2 = as.Date(paste0("2017-", Month_1,"-01"),"%Y-%m-%d")) %>% 
  filter(Year >2016) %>% 
  group_by(Month_2, Year, Age) %>% 
  summarise(Applied = sum(Applied))
```

#

While at first glance, the year over year timing might appear asynchronous, the annual patterns share some parallels. These similarities are more apparent when viewed in 4 distinct tables. 

#

```{r fig.width=10, fig.height=7, out.extra = ''}

SortedTransfersU <- SortedTransfers3 %>% filter(Age == "24 and Under")

myts <- ts(SortedTransfersU$Applied, start=c(2017, 1), end=c(2020, 7), frequency=12)
ggseasonplot(myts, col = colorPalette) + 
  geom_line(size = 1.3) + 
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "bold")) + 
  labs(title = "Transfer Application Flow: \n 24 and Under",
           y = "Applications",
           x = "")  + 
  theme(panel.grid.major = element_blank(), #panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), 
axis.title.x = element_text(color="black", size=12, face="bold"))+ 
  theme_bw(base_size = 12)   + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme(strip.background =element_rect(fill="#FFC13D"))+
  theme(strip.text = element_text(colour = '#323DA5'))

```


```{r  fig.width=10, fig.height=8, out.extra = ''}




ggplot(SortedTransfers3, aes(x = Month_2,y = Applied, group=Age, color=Age)) +
  geom_line(size = 1) +
  #geom_smooth(color = "#323DA5", se = FALSE)+
  facet_wrap(~ Year, ncol = 1.1) +
      labs(title = "Transfer Application Flow",
           # subtitle = "Data plotted by year",
           y = "Applications",
           x = "") + 
  theme_bw(base_size = 12)  +
  scale_x_date(date_labels = "%b", breaks = SortedTransfers3$Month_2) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme(strip.background =element_rect(fill="#FFC13D"))+
  theme(strip.text = element_text(colour = '#323DA5')) + 
  scale_color_manual(values=c("#323DA5", "#FFC13D"))

```

# Conclusions

 
* The application cycle among current undergraduate students begins in August, peaks in November, slows a bit in December, and has a second wave in January. After a short decline in February, we see another spurt in March. Applications trickle in through the spring, slowly declining until summer. The application stream is at its most sluggish through the summer months. 

* This pattern has been the norm since January, 2017. 
* If this pattern remains consistent in 2020, which it may or may not due to the anomalous occurrence of the Covid-19 pandemic, we can expect application movement to shift upward at the end of the summer. We are currently at an annual low point.  



\href{https://www.wrike.com/open.htm?id=533203886}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/fy21-transfer-app-flow}{{\color{blue}{\underline{Github Repository}}}}

```{r eval=FALSE, include=FALSE}
TransferApps <- read.csv("C:/Users/christine.iyer/Box/FY21_Transfer_App_Flow/All_Transfers_Born_After_1990.csv", header = T, stringsAsFactors = F)

TransferApps <- TransferApps %>% 
  mutate(App.Application.Date = as.Date(App.Application.Date, format = "%m/%d/%Y"), 
                                        Created.Date = as.Date(Created.Date, format = "%m/%d/%Y"), 
                                        Birthdate = as.Date(Birthdate, format = "%m/%d/%Y")) %>%
  select(Email, Primary.City, Primary.State.Province, Primary.County, Birthdate, Created.Date, App.Application.Date, App.Application.Status, Student.Stage)
  
Confirmed <- c("Confirmed", "Withdrawn (After Confirmed)")
Enrolled <- c("Enrolled")
Admitted <- c("Admitted (Not Confirmed)", "Withdrawn (After Admitted)", "Withdrawn (After Decision)")
SortedTransfers <- TransferApps %>% 
  mutate(Stage = ifelse(App.Application.Status == "", "Inquiry", ifelse(App.Application.Status == "Enrolled", "Enrolled", 
                                                                         ifelse(App.Application.Status %in% Admitted, "Admitted", 
                                                                                ifelse(App.Application.Status %in% Confirmed, "Confirmed", "Applied")))))

SortedTransfers <-  SortedTransfers %>% 
  
  group_by(Stage, Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province) %>% summarise(n = n()) %>% spread(Stage, n) %>% select(Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province, Inquiry, Applied, Admitted, Confirmed, Enrolled)


```





```{r fig-margin, eval=FALSE, fig.cap="MPG vs horsepower, fig.height=3.5, fig.margin=TRUE, message=FALSE, cache=TRUE, colored by transmission.", fig.width=3.5, include=FALSE}
# __Margin Figures__
# 
# Images and graphics play an integral role in Tufte's work. To place figures in the margin you can use the 
colors <-  c("#F6A704", "#0E1033","#4E7B14","#A92007","#D47E0A")
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
a_a <- ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth(se=FALSE ) +
  theme(legend.position = 'bottom') + theme_bw() +
    scale_color_manual(
        values=colors)
a_a
imgur_image <-
   add_imgur_image(
     image = a_a,
     client_id = "851117406f0b457"
   )

#

#__Save an Image to Email & Compose and Send an Email__

#The plot to the side will be included in an email. 

body_text <-
  glue(
    "


The data he sent makes much more sense. \\
It was excluding students who are not yet captured \\
because the census report is a couple months away. We \\
discussed criteria for a new list which will hopefully \\ 
include students who have deposited and are due to start \\
in the upcoming months. This will give us a second year \\
of applications so we can look at the patterns of ap-\\
plication flow. He's sending the list by EOD tomorrow.



{imgur_image}


Thank you,

Christine Iyer \\
Marketing Data Analyst \\
University of Southern Maine
"
  ) %>% md()

compose_email(body = body_text) %>%
  smtp_send(
    #to = "wrike+into523544264@wrike.com",
    to = "edithbird5@gmail.com",
    #cc = "tracy.st@maine.edu",
    from = "christine.iyer@maine.edu",
    subject = "Project Update",
    credentials = creds_key(id = "gmail")
  )
```




```{r eval=FALSE, fig.fullwidth=TRUE, fig.height=8, include=FALSE}
#tail(SortedTransfers)
SortedTransfers1 <- SortedTransfers %>% 
  mutate_at(6:10, ~replace(., is.na(.), 0)) %>% 
  mutate(
    Applied = sum(Applied) + sum(Admitted)+ sum(Confirmed) + sum(Enrolled), 
    Admitted = sum(Admitted)+ sum(Confirmed) + sum(Enrolled),
    Confirmed =  sum(Confirmed) + sum(Enrolled),
    Enrolled = sum(Enrolled)) %>% 
  group_by(App.Application.Date) %>% 
  summarise(Applied = sum(Applied)) %>% 
  filter(Applied > 0)


SortedTransfers2 <-  SortedTransfers1 %>%
  na.omit() %>% 
  arrange(App.Application.Date)

colorPalette <- c("#323DA5", "#FFC13D", "#4595A4", "#C55A82" )


SortedTransfers3 <- SortedTransfers1 %>% 
  mutate(Month = as.yearmon(App.Application.Date), 
         Year = year(App.Application.Date), 
         Month_1 = month(App.Application.Date), 
         Month_2 = as.Date(paste0("2017-", Month_1,"-01"),"%Y-%m-%d")) %>% 
  filter(Year >2016) %>% 
  group_by(Month_2, Year) %>% 
  summarise(Applied = sum(Applied))



ggplot(SortedTransfers3, aes(x = Month_2,y = Applied)) +
  geom_line(size = 1,color = "#323DA5") +
  #geom_smooth(color = "#323DA5", se = FALSE)+
  facet_wrap(~ Year, ncol = 1.1) +
      labs(title = "Transfer Application Flow",
           # subtitle = "Data plotted by year",
           y = "Applications",
           x = "") + 
  theme_bw(base_size = 12)  +
  scale_x_date(date_labels = "%b", breaks = SortedTransfers3$Month_2) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme(strip.background =element_rect(fill="#FFC13D"))+
  theme(strip.text = element_text(colour = '#323DA5'))

```


```{r r, eval=FALSE, fig.fullwidth=TRUE, fig.height=6, fig.width=10, include=FALSE}

myts <- ts(SortedTransfers3$Applied, start=c(2017, 1), end=c(2020, 7), frequency=12)
ggseasonplot(myts, col = colorPalette) + 
  geom_line(size = 1.3) + 
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "bold")) + 
  labs(title = "Transfer Application Flow",
           y = "Applications",
           x = "")  + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), 
axis.title.x = element_text(color="black", size=12, face="bold"))
```




```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
