---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"

output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: tinytex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(knitr)
library(formatR)
library(blastula)
library(gt)
library(glue)
library(formattable)
library(hms)
library(tidyverse)
library(knitr)
library(ggpubr)
library(lubridate)
library(zoo)
library(forecast)
library(chron)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(tinytex.verbose = TRUE)
```

# FY21 Transfer Student Application Flow

# Description


`r newthought('The purpose of this report ')` is to revisit the flow of applications to the Transfer programs. 
    \href{https://blog.adstage.io/facebook-ads-benchmarks}{{\color{blue}{\underline{FB Newsfeed }}}} CTR overall experienced a 24% drop from July, 2017 - July, 2018.




# Findings

```{r}
TransferApps <- read.csv("C:/Users/christine.iyer/Box/FY21_Transfer_App_Flow/All_Transfers_Born_After_1990.csv", header = T, stringsAsFactors = F)

TransferApps <- TransferApps %>% 
  mutate(App.Application.Date = as.Date(App.Application.Date, format = "%m/%d/%Y"), 
                                        Created.Date = as.Date(Created.Date, format = "%m/%d/%Y"), 
                                        Birthdate = as.Date(Birthdate, format = "%m/%d/%Y")) %>%
  select(Email, Primary.City, Primary.State.Province, Primary.County, Birthdate, Created.Date, App.Application.Date, App.Application.Status, Student.Stage)
  
Confirmed <- c("Confirmed", "Withdrawn (After Confirmed)")
Enrolled <- c("Enrolled")
Admitted <- c("Admitted (Not Confirmed)", "Withdrawn (After Admitted)", "Withdrawn (After Decision)")
SortedTransfers <- TransferApps %>% 
  mutate(Stage = ifelse(App.Application.Status == "", "Inquiry", ifelse(App.Application.Status == "Enrolled", "Enrolled", 
                                                                         ifelse(App.Application.Status %in% Admitted, "Admitted", 
                                                                                ifelse(App.Application.Status %in% Confirmed, "Confirmed", "Applied")))))

SortedTransfers <-  SortedTransfers %>% 
  
  group_by(Stage, Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province) %>% summarise(n = n()) %>% spread(Stage, n) %>% select(Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province, Inquiry, Applied, Admitted, Confirmed, Enrolled)


```





```{r fig-margin, eval=FALSE, fig.cap="MPG vs horsepower, fig.height=3.5, fig.margin=TRUE, message=FALSE, cache=TRUE, colored by transmission.", fig.width=3.5, include=FALSE}
# __Margin Figures__
# 
# Images and graphics play an integral role in Tufte's work. To place figures in the margin you can use the 
colors <-  c("#F6A704", "#0E1033","#4E7B14","#A92007","#D47E0A")
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
a_a <- ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth(se=FALSE ) +
  theme(legend.position = 'bottom') + theme_bw() +
    scale_color_manual(
        values=colors)
a_a
imgur_image <-
   add_imgur_image(
     image = a_a,
     client_id = "851117406f0b457"
   )

#

#__Save an Image to Email & Compose and Send an Email__

#The plot to the side will be included in an email. 

body_text <-
  glue(
    "


The data he sent makes much more sense. \\
It was excluding students who are not yet captured \\
because the census report is a couple months away. We \\
discussed criteria for a new list which will hopefully \\ 
include students who have deposited and are due to start \\
in the upcoming months. This will give us a second year \\
of applications so we can look at the patterns of ap-\\
plication flow. He's sending the list by EOD tomorrow.



{imgur_image}


Thank you,

Christine Iyer \\
Marketing Data Analyst \\
University of Southern Maine
"
  ) %>% md()

compose_email(body = body_text) %>%
  smtp_send(
    #to = "wrike+into523544264@wrike.com",
    to = "edithbird5@gmail.com",
    #cc = "tracy.st@maine.edu",
    from = "christine.iyer@maine.edu",
    subject = "Project Update",
    credentials = creds_key(id = "gmail")
  )
```




```{r fig.fullwidth = TRUE, fig.height=8}
#tail(SortedTransfers)
SortedTransfers1 <- SortedTransfers %>% 
  mutate_at(6:10, ~replace(., is.na(.), 0)) %>% 
  mutate(
    Applied = sum(Applied) + sum(Admitted)+ sum(Confirmed) + sum(Enrolled), 
    Admitted = sum(Admitted)+ sum(Confirmed) + sum(Enrolled),
    Confirmed =  sum(Confirmed) + sum(Enrolled),
    Enrolled = sum(Enrolled)) %>% 
  group_by(App.Application.Date) %>% 
  summarise(Applied = sum(Applied)) %>% 
  filter(Applied > 0)


SortedTransfers2 <-  SortedTransfers1 %>%
  na.omit() %>% 
  arrange(App.Application.Date)

colorPalette <- c("#323DA5", "#FFC13D", "#4595A4", "#C55A82" )


SortedTransfers3 <- SortedTransfers1 %>% 
  mutate(Month = as.yearmon(App.Application.Date), 
         Year = year(App.Application.Date), 
         Month_1 = month(App.Application.Date), 
         Month_2 = as.Date(paste0("2017-", Month_1,"-01"),"%Y-%m-%d")) %>% 
  filter(Year >2016) %>% 
  group_by(Month_2, Year) %>% 
  summarise(Applied = sum(Applied))



ggplot(SortedTransfers3, aes(x = Month_2,y = Applied)) +
  geom_line(size = 1,color = "#323DA5") +
  #geom_smooth(color = "#323DA5", se = FALSE)+
  facet_wrap(~ Year, ncol = 1.1) +
      labs(title = "Transfer Application Flow",
           # subtitle = "Data plotted by year",
           y = "Applications",
           x = "") + 
  theme_bw(base_size = 12)  +
  scale_x_date(date_labels = "%b", breaks = SortedTransfers3$Month_2) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme(strip.background =element_rect(fill="#FFC13D"))+
  theme(strip.text = element_text(colour = '#323DA5'))

```


```{r r, fig.width=10, fig.height=6, fig.fullwidth=TRUE}

myts <- ts(SortedTransfers3$Applied, start=c(2017, 1), end=c(2020, 7), frequency=12)
ggseasonplot(myts, col = colorPalette) + 
  geom_line(size = 1.3) + 
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "bold")) + 
  labs(title = "Transfer Application Flow",
           y = "Applications",
           x = "")  + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), 
axis.title.x = element_text(color="black", size=12, face="bold"))

```


---

```{r}
TransferApps <- read.csv("C:/Users/christine.iyer/Box/FY21_Transfer_App_Flow/All_Transfers_Born_Anytime.csv", header = T, stringsAsFactors = F)

 TransferApps <- TransferApps %>% 
  mutate(App.Application.Date = as.Date(App.Application.Date, format = "%m/%d/%Y"), 
                                        Created.Date = as.Date(Created.Date, format = "%m/%d/%Y"), 
                                        Birthdate = as.Date(Birthdate, format = "%m/%d/%Y")) %>%
  select(Email, Primary.City, Primary.State.Province, Primary.County, Birthdate, Created.Date, App.Application.Date, App.Application.Status, Student.Stage)
  
Confirmed <- c("Confirmed", "Withdrawn (After Confirmed)")
Enrolled <- c("Enrolled")
Admitted <- c("Admitted (Not Confirmed)", "Withdrawn (After Admitted)", "Withdrawn (After Decision)")
SortedTransfers <- TransferApps %>% 
  mutate(Stage = ifelse(App.Application.Status == "", "Inquiry", ifelse(App.Application.Status == "Enrolled", "Enrolled", 
                                                                         ifelse(App.Application.Status %in% Admitted, "Admitted", 
                                                                                ifelse(App.Application.Status %in% Confirmed, "Confirmed", "Applied")))))
unique(SortedTransfers$Stage)
SortedTransfers <-  SortedTransfers %>% 
  
  group_by(Stage, Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province, Birthdate) %>% summarise(n = n()) %>% spread(Stage, n) %>% select(Email,Created.Date, App.Application.Date, Primary.City, Primary.State.Province, Birthdate,Inquiry, Applied, Admitted, Confirmed, Enrolled)


SortedTransfers <- SortedTransfers %>% mutate(AgeAtApp = difftime(App.Application.Date,Birthdate,  units = "weeks"), Age = as.numeric(round(AgeAtApp/52,0)), Age = ifelse(Age < 25, "24 and Under", "25 and Up"))
```

```{r fig.fullwidth=TRUE, fig.height=8, fig.width=6}

#tail(SortedTransfers)
SortedTransfers1 <- SortedTransfers %>% 
  mutate_at(7:11, ~replace(., is.na(.), 0)) %>% 
  mutate(
    Applied = sum(Applied) + sum(Admitted)+ sum(Confirmed) + sum(Enrolled), 
    Admitted = sum(Admitted)+ sum(Confirmed) + sum(Enrolled),
    Confirmed =  sum(Confirmed) + sum(Enrolled),
    Enrolled = sum(Enrolled)) %>% 
  group_by(Age, App.Application.Date) %>% 
  summarise(Applied = sum(Applied)) %>% 
  filter(Applied > 0)


SortedTransfers2 <-  SortedTransfers1 %>%
  na.omit() %>% 
  arrange(App.Application.Date)

colorPalette <- c("#323DA5", "#FFC13D", "#4595A4", "#C55A82" )


SortedTransfers3 <- SortedTransfers1 %>% 
  mutate(Month = as.yearmon(App.Application.Date), 
         Year = year(App.Application.Date), 
         Month_1 = month(App.Application.Date), 
         Month_2 = as.Date(paste0("2017-", Month_1,"-01"),"%Y-%m-%d")) %>% 
  filter(Year >2016) %>% 
  group_by(Month_2, Year, Age) %>% 
  summarise(Applied = sum(Applied))



ggplot(SortedTransfers3, aes(x = Month_2,y = Applied, group=Age, color=Age)) +
  geom_line(size = 1) +
  #geom_smooth(color = "#323DA5", se = FALSE)+
  facet_wrap(~ Year, ncol = 1.1) +
      labs(title = "Transfer Application Flow",
           # subtitle = "Data plotted by year",
           y = "Applications",
           x = "") + 
  theme_bw(base_size = 12)  +
  scale_x_date(date_labels = "%b", breaks = SortedTransfers3$Month_2) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme(strip.background =element_rect(fill="#FFC13D"))+
  theme(strip.text = element_text(colour = '#323DA5')) + 
  scale_color_manual(values=c("#323DA5", "#FFC13D"))

```


```{r , fig.width=10, fig.height=4, fig.fullwidth=TRUE}
SortedTransfersU <- SortedTransfers3 %>% filter(Age == "24 and Under")

myts <- ts(SortedTransfersU$Applied, start=c(2017, 1), end=c(2020, 7), frequency=12)
ggseasonplot(myts, col = colorPalette) + 
  geom_line(size = 1.3) + 
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "bold")) + 
  labs(title = "Transfer Application Flow: \n 24 and Under",
           y = "Applications",
           x = "")  + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), 
axis.title.x = element_text(color="black", size=12, face="bold"))


SortedTransfersO <- SortedTransfers3 %>% filter(Age == "25 and Up")

myts <- ts(SortedTransfersO$Applied, start=c(2017, 1), end=c(2020, 7), frequency=12)
ggseasonplot(myts, col = colorPalette) + 
  geom_line(size = 1.3) + 
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "bold")) + 
  labs(title = "Transfer Application Flow: \nAges 25 and Up",
           y = "Applications",
           x = "")  + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), 
axis.title.x = element_text(color="black", size=12, face="bold"))
```






# Conclusions

 
* Facebook has not published benchmarks for this platform. View and completion rates are \textcolor{red}{slightly down} from this same quarter FY19, but the website has far more unique pageviews.

* In general,
    \href{https://blog.adstage.io/facebook-ads-benchmarks}{{\color{blue}{\underline{FB Newsfeed }}}} CTR overall experienced a 24% drop from July, 2017 - July, 2018.

* Two

\href{https://www.wrike.com/open.htm?id=533203886}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/fy21-transfer-app-flow}{{\color{blue}{\underline{Github Repository}}}}

```{marginfigure, echo = TRUE}
Notice that there is no number preceding the note. $x \in [a, b]$有
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```






```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
